Kit Theory

### 2023-06-21 paper/paper.tex
Update.

\author{Peter Thiemann}
\orcid{0000-0002-9000-1239}                 %% \orcid is optional
\affiliation{
  % \department{Department2a}               %% \department is recommended
  \institution{University of Freiburg}      %% \institution is required
  \country{Germany}                         %% \country is recommended
}
\email{thiemann@informatik.uni-freiburg.de} %% \email is recommended

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stmaryrd}

\usepackage[links]{agda}

% \usepackage{amsmath}
% \usepackage{amsfonts}
% \usepackage{amssymb}

\usepackage{bbold} % lower case mathbb letters

% \usepackage{cite}
% \usepackage{DejaVuSansMono}
% \usepackage{alphabeta} % Make greek letter macros also work in text-mode.

\usepackage{microtype}
\DisableLigatures[-]{encoding=T1}

@@

  \section{Introduction}
  \newpage

  \section{Syntax}
  \subsection{Library}
  \KVariables
  \KSortTy
  \KTerms
  \subsection{System F}
  \FSort
  \FSyntax
  \FTerms

>>>>

% \author{Peter Thiemann}
% \orcid{0000-0002-9000-1239}                 %% \orcid is optional
% \affiliation{
%   % \department{Department2a}               %% \department is recommended
%   \institution{University of Freiburg}      %% \institution is required
%   \country{Germany}                         %% \country is recommended
% }
% \email{thiemann@informatik.uni-freiburg.de} %% \email is recommended

\usepackage{tcolorbox}
% \newenvironment{LibCode}{%
%   \begin{tcolorbox}[boxrule=0.5pt,top=0pt,left=0pt,right=2.5pt,boxsep=0pt]\vspace{-0.5\baselineskip}}{%
%   \end{tcolorbox}}
\newenvironment{LibCode}{%
  \begin{tcolorbox}[boxrule=0.0pt,frame hidden,top=0pt,left=0pt,right=2.5pt,boxsep=0pt]\vspace{-0.5\baselineskip}}{%
  \end{tcolorbox}}

@@

  \section{Introduction}
  Formalizing metatheory of programming languages in a proof assistant 
  requires to deal with variables, binders and substitution.

  In most languages those constructs behave uniformly,
  i.e. substitution is only concerned with variables and binders and
  behaves homomorphic on all other syntax constructors.

  Intrinsic typing

  \begin{enumerate}
  \item DeBruijn
  \item Intrinsic vs Extrinsic
  \item Reduction under binder
  \end{enumerate}

  \subsection{Contributions}
  \begin{enumerate}
  \item
    a multi-sorted approach to extrinsic typing;
  \item
    a multi-sorted extension of McBride's kits to unify renamings and substitutions and their metatheory;
  \item
    a kit abstraction for composition and it's metatheory, unifying the four combinations of renamings and substitutions;
  \item
    a kit abstraction for typing relations, unifying type preservation of renaming and substitution into a single lemma;
  \item
    an Agda-implementation featuring derived term-kits, representation
    independence for substitutions and typing contexts, heterogeneous
    equality, independence of functional extensionality, case studies
    on System F, dependent lambda calculus, pattern matching, linear
    types.
  \end{enumerate}

  \newpage

  \section{Syntax}
  The following shows a typical intrinsically-scoped syntax of System F:
  \FUnsortedSyntax

  \texttt{Type}s are indexed by the number of free type variables \texttt{n}.
  \texttt{Expr}essions are additionally indexed by the number of free expression variables \texttt{m}.
  Variables are represented as DeBruijn-indices, where \texttt{Fin n} is the type of \texttt{n} elements.

  This style of syntax comes with multiple drawbacks:
  \begin{itemize}
  \item Bad scaling for automation
  \item Multiple substitions require interaction lemmas
  \end{itemize}

  % Instead we define a single term type which is indexed by the sort of
  % syntax, i.e.\ whether the term is a kind, type, or expression:
  To avoid these drawbacks, we define a single term type \texttt{S~⊢~s} that is indexed by its sort \texttt{s},
  i.e.\ whether the term is a kind, type, or expression, and the sorts of its free variables \texttt{S}:

  \begin{LibCode}
  \KSortTy
  \end{LibCode}

  \FSort
  \FSyntax
  The variable constructor \texttt{'\_} takes a sorted DeBruijn-index \texttt{S~∋~s}.
  Since the \texttt{Sort}s in \texttt{S} are restricted to the sort-type \texttt{Var}, it is not possible to construct kind-variables.

  \subsection{Library}
  \KVariables
  \KSortTy
  \KTerms
  \subsection{System F}
  \FSort
  \FSyntax
  \FTerms
